MultiATSM package - General Guidelines

### 2022-04-14 inst/doc/my-vignette.Rmd
version 0.2.1

The *MultiATSM* package provides several model outputs from various single and multi-country affine term structure of interest models (ATSMs). All the frameworks of this package are based on the unspanned economic risk framework from @JoslinPriebschSingleton2014 (JPS, 2014). In essence, these models assume the absence of arbitrage opportunities, consider a linear state space representations of the yield curve dynamics and offer a tractable approach to simultaneously combine the traditional yield curve factors (spanned factors) along with economic and financial variables (unspanned factors).

@@

In its current version, the *MultiATSM* package can generate the outputs of 8 different classes of ATSMs. More specifically, the *MultiATSM* includes models in which the estimation is done on a *country-by-country* basis - as in JPS (2014)  - or *jointly* for all the countries of the economic system - as in @JotikasthiraLeLundblad2015 (JLL, 2015) and @CandelonMoura2021 (CM, 2021).  In all cases, the risk factors dynamics under the $P$-measure follows a VAR(1) model of some sort. The table below summarizes the general features of each one of the models available at this package.

@@

# Empty columns
EmptyCol <- c("", "", "", "", "", "", "", "") 
Tab$EmptyCol0 <- EmptyCol
# P-dynamics + 2 empty spaces
Tab$PdynIndUnco <- c("x", "x", "", "", "", "", "", "")
Tab$PdynIndCo <- c("", "", "", "", "", "", "", "")
Tab$PdynJointUnco <- c("", "", "x", "", "", "", "", "")
Tab$PdynJointJLL <- c("", "", "", "", "", "x", "x", "x")
Tab$PdynJointGVAR <- c("", "", "", "x", "x", "", "", "")
Tab$EmptyCol1 <- EmptyCol
Tab$EmptyCol2 <- EmptyCol
# Q-dynamics + 2 empty spaces
Tab$QdynInd <- c("x", "", "", "x", "", "", "", "")   
Tab$QdynJoint <- c("", "x", "x", "", "x", "x", "x", "x") 
Tab$EmptyCol3 <- EmptyCol
Tab$EmptyCol4 <- EmptyCol
# Sigma + 2 empty spaces
Tab$Ponly <-  c("", "", "", "", "", "x", "x", "")
Tab$PandQ <- c("x", "x", "x", "x", "x", "", "", "x")
Tab$EmptyCol5 <- EmptyCol
Tab$EmptyCol6 <- EmptyCol
# Dominant Unit
Tab$DomUnit <- c("", "", "", "", "", "x", "", "x")

@@

## Package data-set{#S:SectionDataPackage}
The *MultiATSM* package contains the four data-sets used in CM (2021). The first set of data comprises several time series of zero-coupon bonds yields from four emerging markets: China, Brazil, Mexico, and Uruguay. It is worth noting that this package requires *(i)* for estimation purposes, the maturities of the bond yields to be the same for all countries (although the function *DataForEstimation* handles different maturities across countries as inputs, the outputs generated by this same function are bond yields of the same maturities for all the economies); *(ii)* bond yields to be expressed in percentage terms (and not in basis points) per annum. The *MultiATSM* package does not support a routine to bootstrap zero-coupon yields from coupon bonds. This data manipulation procedure must be handled by the user herself, if necessary.  
```{r}
data('CM_Yields')
```

The second group of data concerns the time series of the risk factors. Specifically, along the terminology defined in JPS (2014), this data-set contains *(i)* country-specific spanned factors (denoted by level, slope, and curvature - see Section \@ref(S:SpaFac) for a more detailed description) and *(ii)* an array of country-specific and global unspanned factors (namely, some measure of economic growth and inflation). Similarly to the case of the bond yields data, the measures of economic and financial variables must be constructed by the user.
```{r}
data('CM_Factors')
```

The two last block of data are necessary for the estimation of the GVAR-based models. The trade flows database
presents the sum of the value of all goods imports and exports between any two countries of the sample on yearly basis since 1948. All the values are free on board and are expressed in U.S. dollars. This data is used to construct the transition matrix of the GVARs models.  
```{r}
data('CM_Trade')
```

The GVAR factors database casts country-specific lists of all the factors that are used in the estimation of each country's VARX(1,1,1). A specific function for computing the star risk factors is detailed the Section \@ref(S:SectionGVAR). 
```{r}
data('CM_Factors_GVAR')
```

## Import data from Excel files {#S:SectionImport}
This package also offers an automatized procedure to extract data from Excel files and to, subsequentially, prepare the risk factors database that are directly used in the model estimation. The use of the package functions requires that the databases *(i)* are constructed in separate Excel files for the unspanned factors, the term structure data, and the measures of interdependence (for the GVAR-based models); *(ii)* contain, in each Excel file, one separate tab per country (in addition to the global variables, in the case of the unspanned factors database); and *(iii)* have identical variable labels across all the tabs within each file. For illustration, see the Excel file available at the package.
One example of list of inputs to be provided is, for instance,
```{r}
Initial_Date <- "2006-09-01" # Format "yyyy-mm-dd"
Final_Date <- "2019-01-01" # Format "yyyy-mm-dd"
DataFrequency <- "Monthly"
GlobalVar <- c("GBC", "VIX") # Global Variables
DomVar <- c("Eco_Act", "Inflation", "Com_Prices", "Exc_Rates") #  Domestic variables
N <-  3 # Number of spanned factors per country
Economies <- c("China", "Mexico", "Uruguay", "Brazil", "Russia")
ModelType <- "JPS"
```

@@

- **Model type**: a string-vector containing the label of the model to be estimated (as per described in Table \@ref(tab:ModFea)); 
- **Frequency of the data**: a string-vector that specifies the frequency of the time series data. The available options are: *"Annually"*, *"Quarterly"*, *"Monthly"*, *"Weekly"*, *"Daily Business Days"*, and *"Daily All Days"*;
- **Economies**: a string-vector containing the names of the economies which are part of the economic system;
- **Number of spanned factors (N)**: number of country-specific spanned factors. In this package, *N* is assumed to be equal across countries;
- **Global variables**: a string-vector containing the labels of the global unspanned factors used in the model estimation;
- **Domestic variables**: a string-vector containing the labels of the domestic unspanned factors used in the model estimation;
- **Bond yield set of maturities**: a numerical-vector containing the maturities of the yields used in the model estimation. The units of this vector must be expressed in *years*. Alternatively, the user can rely on the *Maturities* routine to extract the the bond maturities form the time series of bond yields (see the documentation of the *Maturities* function). In this case, the user must specify the **unit in which the label of the bond yields** are expressed, e.g. if the label of the 10-years bond is selected as *Y120M* (*Y10y*), then the option *Month* (*Year*) must be selected;
- **Factor labels**: a string-list based which contains the labels of all the variables present in the model. This input is particularly useful for constructing the plots. The routine *LabFac* provides the desired list of factor labels;
- **Stationarity constraint under the $Q$-dynamics**: a binary variable which takes value equal to "1" if the user wishes the largest eigenvalue under the $Q$-measure to be strictly smaller than 1. Otherwise, this same variable must be set to "0";
- **Output label**: a single element string-vector which contains the of the name that appears in the file name that stores the model outputs.

@@

- **Economies**: a string-vector containing the names of the economies as described above;  
- **GVAR list of risk factors**:  a list of risk factors sorted by country in addition to the global variables. See function *DatabasePrep*;
- **VARX type**: a string-vector containing the desired estimated form of the VARX(1,1,1). Two possibilities are available. The *"unconstrained"* form estimates the model without any constrains using standard OLS regressions for each one of the model equations. The *"constrained"* form prevents foreign-spanned-factors to impact any domestic factor. In such a case, the VARX(1,1,1) is estimated by restricted least squares.

```{r}
GVARinputs <- list()
GVARinputs$Economies <- Economies
GVARinputs$GVARFactors <- FactorsGVAR
GVARinputs$VARXtype <- "unconstrained"
```

@@

- **JLL type**: a string-vector containing the label of the JLL model to be estimated (as described in Table \@ref(tab:ModFea));
- **Economies**: a string-vector containing the names of the economies as described above;
- **Dominant Country**: a string-vector containing the name of the economy which is assigned as the dominant country (applicable for the *JLL original* and *JLL jointSigma* models) or "None" (applicable for the *JLL NoDomUnit*).
 - **Wish the estimation of the sigmas matrices**: this is a binary variable which assume value equal to 1 if the user wishes the estimation of all JLL sigma matrices (i.e. variance-covariance and the Cholesky factorization matrices) and, 0 otherwise. The estimation of the sigma matrices can take several minutes;
- **Sigma of the non-orthogonalized variance-covariance matrix**: to save time, the user may provide the variance-covariance matrix from the non-orthogonalized dynamics. Otherwise, this input should be set as *NULL*.

@@

### Out-of-sample forecast settings
To perform out-of-sample forecasts, the following list-based features have to be detailed:

@@

```{r, fig.cap = "Yield loading on the spanned factors", echo=FALSE}
LabSpaFac <- c("Level", "Slope", "Curvature")
N <- length(LabSpaFac)

@@

## The P-dynamics estimation
As presented in Table \@ref(tab:ModFea), the dynamics of the risk factors under the $P$-measure evolves according to a VAR(1) model, which may be fully unrestricted (as in the case of the JPS-related models) or somewhat restricted (as in the GVAR and JLL frameworks). Below, the usage of each one of these dimensions are illustrated.

@@

In both cases, the outputs generated are the vector of intercepts in addition to the feedback and the variance-covariance matrices.

### GVAR {#S:SectionGVAR}
The estimation of a GVAR model requires defining a measure of interdependence among the countries of the economic system. This information is reported in the transition matrix, the entries of which reflect the degree of interconnections of two entities of this same economic system. In this package, the illustration of the transition matrix is based on the average of the cross-borders trade flow weights for the period spanning the years from 2006 to 2019. Note that each row sums up to 1.

@@

### Optimization parameters
JPS (2014) requires the estimation of a set of parameters containing 6 elements, namely: the risk-neutral
long-run mean of the short rate (*r0*), the risk-neutral feedback matrix (*K1XQ*), the variance-covariance matrix (*SSZ*) from the VAR processes, the standard deviation of the errors from the portfolios of yields observed with error (*se*), in addition to the intercept (*K0Z*) and the feedback (*K1Z*) matrices of the physical dynamics. Each one of these parameters must be cast in a individual list that should contain the *(i)* the starting value of the parameter (if any); *(ii)* the variable label followed by a ':' and a type of constraint; *(iii)* a lower bound (if any), and *(iv)* an upper bound (if any). The variable labels of *r0*, *se*, *K0Z* and *K1Z* should be preceded by the symbol @ as manner to account for the fact that the solution for these parameters are known in closed-form. For the remaining ones (*K1XQ* and *SSZ*), @LeSingleton2018 provide standardized routines (already incorporated in this package) to set good initial values so that the optimization process runs fast.

@@

  # 6) Optimization of the model
  if (ModelType == 'JPS' || ModelType == 'JPS jointP' || ModelType == "GVAR sepQ"){
    ModelParaList[[ModelType]][[Economies[i]]] <- Optimization(f, tol, varargin, FactorLabels, Economies, ModelType)$Summary
  }else{ ModelParaList[[ModelType]] <- Optimization(f, tol, varargin, FactorLabels, Economies, ModelType, JLLinputs)$Summary}

@@

## Paper replications
### Joslin, Priebisch and Singleton (2014)
To the best of my knowledge, the original data-set used in @JoslinPriebschSingleton2014 is not publicly available. Nevertheless, there exists an alternative source of data that closely matches JPS (2014) in terms of the construction method and the sample period. This database is constructed by @BauerRudebusch2017 (BR, 2017) and is available at [Bauer's website](https://www.michaeldbauer.com/publication/spanning-puzzle/). In that paper, BR (2017) investigate whether macro-finance term structure models better suit the unspanned macro risk framework by JPS (2014) or the earlier traditional spanned settings as the one by @AngPiazzesi2003JME. Accordingly, BR (2017) intend to replicate some of the empirical results reported in JPS (2014). The R-code used by BR (2017) is also available at available at [Bauer's website](https://www.michaeldbauer.com/publication/spanning-puzzle/).

@@

It is relevant to highlight that the script above makes use of the principal component weight provided by BR (2017). Such a matrix is simply a scaled-up version of the one provided by the function *pca_weights_one_country* of this package. Accordingly, despite the numerical differences on the weight matrices, both methods generate time series of spanned factors which are perfectly correlated. Another difference between the two approaches relates to the construction form of the log-likelihood function (llk): while in the BR (2017) code the llk is expressed in terms of portfolio of yields, the *MultiATSM* package generates this same input directly as a function of observed yields (i.e. both procedures lead to equivalent llk up to the Jacobian term).

@@

@@

# 6) Optimization of the model
ModelParaList[[ModelType]] <- Optimization(f, tol, varargin, FactorLabels, Economies, ModelType, JLLinputs)$Summary

>>>>

The *MultiATSM* package provides several model outputs from various single and multi-country affine term structure of interest models (ATSMs). All the frameworks of this package are based on the unspanned economic risk framework from @JoslinPriebschSingleton2014 (JPS, 2014). In essence, these models assume the absence of arbitrage opportunities, consider a linear state space representation of the yield curve dynamics and offer a tractable approach to simultaneously combine the traditional yield curve factors (spanned factors) along with economic and financial variables (unspanned factors).

@@

In its current version, the *MultiATSM* package can generate the outputs of 8 different classes of ATSMs. More specifically, the *MultiATSM* includes models in which the estimation is done on a *country-by-country* basis - as in JPS (2014)  - or *jointly* for all the countries of the economic system - as in @JotikasthiraLeLundblad2015 (JLL, 2015) and @CandelonMoura2021 (CM, 2021).  In all cases, the risk factor dynamics under the $P$-measure follow a VAR(1) model of some sort. The table below summarizes the general features of each one of the models available at this package.

@@

# Empty columns
EmptyCol <- c("", "", "", "", "", "", "", "") 
Tab$EmptyCol0 <- EmptyCol
# P-dynamics + 2 empty spaces
Tab$PdynIndUnco <- c("x", "", "", "", "", "", "", "")
Tab$PdynIndCo <- c("", "", "", "", "", "", "", "")
Tab$PdynJointUnco <- c("", "x", "x", "", "", "", "", "")
Tab$PdynJointJLL <- c("", "", "", "", "", "x", "x", "x")
Tab$PdynJointGVAR <- c("", "", "", "x", "x", "", "", "")
Tab$EmptyCol1 <- EmptyCol
Tab$EmptyCol2 <- EmptyCol
# Q-dynamics + 2 empty spaces
Tab$QdynInd <- c("x", "x", "", "x", "", "", "", "")   
Tab$QdynJoint <- c("", "", "x", "", "x", "x", "x", "x") 
Tab$EmptyCol3 <- EmptyCol
Tab$EmptyCol4 <- EmptyCol
# Sigma + 2 empty spaces
Tab$Ponly <-  c("", "", "", "", "", "x", "x", "")
Tab$PandQ <- c("x", "x", "x", "x", "x", "", "", "x")
Tab$EmptyCol5 <- EmptyCol
Tab$EmptyCol6 <- EmptyCol
# Dominant Unit
Tab$DomUnit <- c("", "", "", "", "", "x", "", "x")

@@

## Package data-set{#S:SectionDataPackage}
The *MultiATSM* package contains the four data-sets used in CM (2021). The first set of data comprises several time series of zero-coupon bond yields from four emerging markets: China, Brazil, Mexico, and Uruguay. It is worth noting that this package requires *(i)* for estimation purposes, the maturities of the bond yields to be the same for all countries (although the function *DataForEstimation* handles different maturities across countries as inputs, the outputs generated by this same function are bond yields of the same maturities for all the economies); *(ii)* bond yields to be expressed in percentage terms (and not in basis points) per annum. The *MultiATSM* package does not support a routine to bootstrap zero-coupon yields from coupon bonds. This data manipulation procedure must be handled by the user herself, if necessary.  
```{r}
data('CM_Yields')
```

The second group of data concerns the time series of the risk factors. Specifically, along the terminology defined in JPS (2014), this data-set contains *(i)* country-specific spanned factors (denoted by level, slope, and curvature - see Section \@ref(S:SpaFac) for a more detailed description) and *(ii)* an array of country-specific and global unspanned factors (namely, some measure of economic growth and inflation). Similarly to the case of the bond yield data, the measures of economic and financial variables must be constructed by the user.
```{r}
data('CM_Factors')
```

The two last blocks of data are necessary for the estimation of the GVAR-based models. The trade flows database
presents the sum of the value of all goods imports and exports between any two countries of the sample on a yearly basis since 1948. All the values are free on board and are expressed in U.S. dollars. These data are used to construct the transition matrix of the GVARs models.  
```{r}
data('CM_Trade')
```

The GVAR factors database casts country-specific lists of all the factors that are used in the estimation of each country's VARX(1,1,1). A specific function for computing the star risk factors is detailed in the Section \@ref(S:SectionGVAR). 
```{r}
data('CM_Factors_GVAR')
```

## Import data from Excel files {#S:SectionImport}
This package also offers an automatized procedure to extract data from Excel files and to, subsequentially, prepare the risk factor databases that are directly used in the model estimation. The use of the package functions requires that the databases *(i)* are constructed in separate Excel files for the unspanned factors, the term structure data, and the measures of interdependence (for the GVAR-based models); *(ii)* contain, in each Excel file, one separate tab per country (in addition to the global variables, in the case of the unspanned factors' database); and *(iii)* have identical variable labels across all the tabs within each file. For illustration, see the Excel file available at the package.
One example of list of inputs to be provided is, for instance,
```{r}
Initial_Date <- "2006-09-01" # Format "yyyy-mm-dd"
Final_Date <- "2019-01-01" # Format "yyyy-mm-dd"
DataFrequency <- "Monthly"
GlobalVar <- c("GBC", "VIX") # Global Variables
DomVar <- c("Eco_Act", "Inflation", "Com_Prices", "Exc_Rates") #  Domestic variables
N <-  3 # Number of spanned factors per country
Economies <- c("China", "Mexico", "Uruguay", "Brazil", "Russia")
ModelType <- "JPS"
```

@@

- **Model type**: a string-vector containing the label of the model to be estimated (as per described in Table \@ref(tab:ModFea)); 
- **Frequency of the data**: a string-vector that specifies the frequency of the time series data. The available options are: *"Annually"*, *"Quarterly"*, *"Monthly"*, *"Weekly"*, *"Daily Business Days"*, and *"Daily All Days"*;
- **Economies**: a string-vector containing the names of the economies which are part of the economic system;
- **Number of spanned factors (N)**: number of country-specific spanned factors. In this package, *N* is assumed to be equal across countries;
- **Global variables**: a string-vector containing the labels of the global unspanned factors used in the model estimation;
- **Domestic variables**: a string-vector containing the labels of the domestic unspanned factors used in the model estimation;
- **Bond yield set of maturities**: a numerical-vector containing the maturities of the yields used in the model estimation. The units of this vector must be expressed in *years*. Alternatively, the user can rely on the *Maturities* routine to extract the bond maturities from the time series of bond yields (see the documentation of the *Maturities* function). In this case, the user must specify the **unit in which the label of the bond yields** are expressed, e.g. if the label of the 10-years bond is selected as *Y120M* (*Y10y*), then the option *Month* (*Year*) must be selected;
- **Factor labels**: a string-list based which contains the labels of all the variables present in the model. This input is particularly useful for constructing the plots. The routine *LabFac* provides the desired list of factor labels;
- **Stationarity constraint under the $Q$-dynamics**: a binary variable which takes value equal to "1" if the user wishes the largest eigenvalue under the $Q$-measure to be strictly smaller than 1. Otherwise, this same variable must be set to "0";
- **Output label**: a single element string-vector which contains the of the name that appears in the file name that stores the model outputs.

@@

- **Economies**: a string-vector containing the names of the economies as described above;  
- **GVAR list of risk factors**:  a list of risk factors sorted by country in addition to the global variables. See function *DatabasePrep*;
- **VARX type**: a string-vector containing the desired estimated form of the VARX(1,1,1). Two possibilities are available. The *"unconstrained"* form estimates the model without any constrains, using standard OLS regressions for each model equation. The *"constrained: Spanned Factors"* form prevents foreign-spanned-factors to impact any domestic factor in the feedback matrix, whereas *"constrained: '* followed by the name of the risk factor restricts this same factor to be influenced only by its own lagged values and the lagged values of its own star variables. In the last two cases, the VARX(1,1,1) is estimated by restricted least squares.

```{r}
GVARinputs <- list()
GVARinputs$Economies <- Economies
GVARinputs$GVARFactors <- FactorsGVAR
GVARinputs$VARXtype <- "constrained: Inflation"
```

@@

- **JLL type**: a string-vector containing the label of the JLL model to be estimated (as described in Table \@ref(tab:ModFea));
- **Economies**: a string-vector containing the names of the economies as described above;
- **Dominant Country**: a string-vector containing the name of the economy which is assigned as the dominant country (applicable for the *JLL original* and *JLL jointSigma* models) or "None" (applicable for the *JLL NoDomUnit*).
 - **Wish the estimation of the sigmas matrices**: this is a binary variable which assumes value equal to 1 if the user wishes the estimation of all JLL sigma matrices (i.e. variance-covariance and the Cholesky factorization matrices) and, 0 otherwise. The estimation of the sigma matrices can take several minutes;
- **Sigma of the non-orthogonalized variance-covariance matrix**: to save time, the user may provide the variance-covariance matrix from the non-orthogonalized dynamics. Otherwise, this input should be set as *NULL*.

@@

### Out-of-sample forecast settings
To perform out-of-sample forecasts of bond yields, the following list-based features have to be detailed:

@@

```{r, fig.cap = "Yield loadings on the spanned factors", echo=FALSE}
LabSpaFac <- c("Level", "Slope", "Curvature")
N <- length(LabSpaFac)

@@

## The P-dynamics estimation
As presented in Table \@ref(tab:ModFea), the dynamics of the risk factors under the $P$-measure evolve according to a VAR(1) model, which may be fully unrestricted (as in the case of the JPS-related models) or somewhat restricted (as in the GVAR and JLL frameworks). Below, the usage of each of these dimensions are illustrated.

@@

In both cases, the outputs generated are the vector of intercepts and both the feedback and variance-covariance matrices.

### GVAR {#S:SectionGVAR}
The estimation of a GVAR model requires defining a measure of interdependence among the countries of the economic system. This information is reported in the transition matrix, the entries of which reflect the degree of interconnection of two entities of this same economic system. In this package, the illustration of the transition matrix is based on the average of the cross-border trade flow weights for the period spanning the years from 2006 to 2019. Note that each row sums up to 1.

@@

### Optimization parameters
JPS (2014) requires the estimation of a set of parameters containing 6 elements, namely: the risk-neutral
long-run mean of the short rate (*r0*), the risk-neutral feedback matrix (*K1XQ*), the variance-covariance matrix (*SSZ*) from the VAR processes, the standard deviation of the errors from the portfolios of yields observed with error (*se*), in addition to the intercept (*K0Z*) and the feedback (*K1Z*) matrices of the physical dynamics. Each of these parameters must be cast in an individual list that should contain the *(i)* the starting value of the parameter (if any); *(ii)* the variable label followed by a ':' and a type of constraint; *(iii)* a lower bound (if any), and *(iv)* an upper bound (if any). The variable labels of *r0*, *se*, *K0Z* and *K1Z* should be preceded by the symbol @ as a manner to account for the fact that the solution of these parameters are known in closed-form. For the remaining ones (*K1XQ* and *SSZ*), @LeSingleton2018 provide standardized routines (already incorporated in this package) to set good initial values so that the optimization process runs fast.

@@

  # 6) Optimization of the model
  if (ModelType == 'JPS' || ModelType == 'JPS jointP' || ModelType == "GVAR sepQ"){
    ModelParaList[[ModelType]][[Economies[i]]] <- Optimization(f, tol, varargin, FactorLabels, Economies, ModelType, JLLinputs, GVARinputs)$Summary
  }else{ ModelParaList[[ModelType]] <- Optimization(f, tol, varargin, FactorLabels, Economies, ModelType, JLLinputs, GVARinputs)$Summary}

@@

## Paper replications
### Joslin, Priebisch and Singleton (2014)
To the best of my knowledge, the original data-set used in @JoslinPriebschSingleton2014 is not publicly available. Nevertheless, there exists an alternative source of data that closely matches JPS (2014) in terms of the construction method and the sample period. This database is constructed by @BauerRudebusch2017 (BR, 2017) and is available at [Bauer's website](https://www.michaeldbauer.com/publication/spanning-puzzle/). In that paper, BR (2017) investigate whether macro-finance term structure models better suit the unspanned macro risk framework by JPS (2014) or the earlier traditional spanned settings as the one by @AngPiazzesi2003JME. Accordingly, BR (2017) intend to replicate some of the empirical results reported in JPS (2014). The R-code used by BR (2017) is also available at [Bauer's website](https://www.michaeldbauer.com/publication/spanning-puzzle/).

@@

It is relevant to highlight that the script above makes use of the principal component weights provided by BR (2017). Such a matrix is simply a scaled-up version of the one provided by the function *pca_weights_one_country* of this package. Accordingly, despite the numerical differences on the weight matrices, both methods generate time series of spanned factors which are perfectly correlated. Another difference between the two approaches relates to the construction form of the log-likelihood function (llk): while in the BR (2017) code the llk is expressed in terms of a portfolio of yields, the *MultiATSM* package generates this same input directly as a function of observed yields (i.e. both procedures lead to equivalent llk up to the Jacobian term).

@@

varargin <- list()
varargin$K1XQ <-list(K1XQ, VarLab[[ModelType]][["K1XQ"]], NULL , NULL)
varargin$SSZ <- list(SSZ, VarLab[[ModelType]][["SSZ"]], NULL, NULL)
varargin$r0 <- list(NULL, VarLab[[ModelType]][["r0"]], NULL, NULL)
varargin$se <- list(NULL, VarLab[[ModelType]][["se"]], 1e-6, NULL)
varargin$K0Z <- list(NULL, VarLab[[ModelType]][["K0Z"]], NULL, NULL)
varargin$K1Z <- list(NULL, VarLab[[ModelType]][["K1Z"]], NULL, NULL)
varargin$OptRun <-  c("iter off")

@@

# 6) Optimization of the model
ModelParaList[[ModelType]] <- Optimization(f, tol, varargin, FactorLabels, Economies, ModelType, JLLinputs, GVARinputs)$Summary
